Sketch of DP - Bayesian Inference

### 2018-07-14 main-sketch.tex
update bib
abstract second pass

\begin{abstract}

  Bayesian inference is a statistical method which allows to derive
  a \emph{posterior} distribution over a parameter, 
  starting from a \emph{prior} distribution and observed data.
  Many works have focused on making this
  process differentially private adding noise on the parameters
  representing the distributions\todo{cite?}.
  % Also,  the sensitivity 
  % was computed w.r.t. a numeric norm over the space of the numeric parameters
  % characterizing the output distribution.
  Also, the accuracy was measured
  using metrics on the space of the numeric parameters representing the
  posterior distribution, e.g. $\ell_1$-norm \todo{cite}.

  We designed a new mechanism for differentially private Bayesian inference
  where the noise is proportional to a smooth sensitivity computed w.r.t a metric
  on probability distributions; we also measured the accuracy of the process
  by using a metric over probability measures.
  We compared the accuracy of this approach with the one based on $\ell_1$-norms.
  Experimental results show that in some situations the former outperforms the latter.

@@

The posterior belief about parameters $\xis$ is inferred from the group of sensitive data. Because it is usually published in form of a distribution, for example, $\betad(\alpha',\beta'), \cdots,$ itself can relieve a lot of information about sensitive data. So, the sensitive information we want to protect here is the posterior belief, i.e., $Pr(\xis | \textbf{x})$, rather than just a sample drew from it\cite{foulds2016theory}. Then it will be better if we can use a distance over two distributions to measure the accuracy than a distance over just parameters or values when we are protecting a distribution, for instance, Hellinger distance in our paper. When we measure the accuracy between true posterior and protected posterior using Hellinger distance, it would be better we can have a protection mechanism based on Hellinger distance. However, current mechanisms are mainly based on $l_1$ norm by Laplace mechanism \cite{zhang2016differential}. That's why we design our exponential mechanism over Hellinger distance to protect the whole posterior distribution.

>>>>

\begin{abstract}
  Bayesian inference is a statistical method which allows to derive a
\emph{posterior} distribution over a parameter, starting from a
\emph{prior} distribution and observed data.  Many works have focused
on making this process differentially private adding noise on the
parameters representing the distributions\todo{cite?}.  Also, the
accuracy was measured using metrics on  the numeric
parameters representing the posterior distribution, e.g. $\ell_1$-norm
\todo{cite?}.

In this work we present a new mechanism for differentially private Bayesian
inference where the noise is added w.r.t  a smooth
sensitivity computed with a metric on probability distributions.
We also measure the accuracy of the process by using a metric over
probability measures.  We compared the accuracy of this approach with
the one based on the $\ell_1$-norm.  We present experimental results
showing that the former outperforms the latter.

@@

The posterior belief about parameters $\xis$ is inferred from the group of sensitive data. Because it is usually published in form of a distribution, for example, $\betad(\alpha',\beta'), \cdots,$ itself can relieve a lot of information about sensitive data. So, the sensitive information we want to protect here is the posterior belief, i.e., $Pr(\xis | \textbf{x})$, rather than just a sample drew from it\cite{foulds2016theory}. Then it will be better if we can use a distance over two distributions to measure the accuracy than a distance over just parameters or values when we are protecting a distribution, for instance, Hellinger distance in our paper. When we measure the accuracy between true posterior and protected posterior using Hellinger distance, it would be better we can have a protection mechanism based on Hellinger distance. However, current mechanisms are mainly based on $l_1$ norm by Laplace mechanism \cite{zhang2016differential} \cite{xiao2012bayesian}. That's why we design our exponential mechanism over Hellinger distance to protect the whole posterior distribution.
